Comparison of two object-oriented languages: C++ and Ruby

### 2011-12-27 paper.tex
Added basic information about inheritance in Ruby

\subsection{Inheritance}

@@

\section{References}
http://www.ruby-lang.org/en/about/
http://www.cplusplus.com/info/history/
http://publib.boulder.ibm.com/infocenter/lnxpcomp/v8v101/index.jsp?topic=%2Fcom.ibm.xlcpp8l.doc%2Flanguage%2Fref%2Fcplr142.htm
http://www.klankboomklang.com/2007/10/05/the-metaclass/

>>>>

\subsection{Inheritance}
In Ruby, a class can only inherit from a single other class. Some other languages like C++ support multiple inheritance, a feature that allows classes to inherit features from multiple classes.
\begin{lstlisting}[language=Ruby]
class Animal
	def breath
		puts "Breathe"
	end
	def speak
		puts "Random noise"
	end
end

class Cat < Animal
	def speak
		puts "Meow"
	end
end
\end{lstlisting}
When using these two classes, one can see that methods will be overriden:
\begin{lstlisting}[language=Ruby]
cat = Cat.new
cat.speak
cat.breath
\end{lstlisting}
This will output:
\begin{lstlisting}
Random noise
Breathe
\end{lstlisting}
Inheritance in C++ is more advanced as it supports multiple inheritance.

Ruby mixin's.

\subsection{Access control}

\subsection{The use of super and this/self}

\subsection{Polymorphism}

\subsection{Interfaces}

\subsection{Reflection}

\subsection{Clonable objects}

\subsection{Everything is an object?}

@@

\section{References}
http://www.ruby-lang.org/en/about/
http://www.cplusplus.com/info/history/
http://publib.boulder.ibm.com/infocenter/lnxpcomp/v8v101/index.jsp?topic=\%2Fcom.ibm.xlcpp8l.doc\%2Flanguage\%2Fref\%2Fcplr142.htm
http://www.klankboomklang.com/2007/10/05/the-metaclass/
http://ruby-extra.rubyforge.org/classes/Object.html
http://www.wikyblog.com/AmanKing/Metaclass_in_Ruby
http://www.klankboomklang.com/2007/10/12/objects-classes-and-jruby-internals/
http://shiningthrough.co.uk/A-comparison-of-Ruby-pass-by-reference-and-C++-pass-by-reference
http://rubylearning.com/satishtalim/ruby_inheritance.html
